### 2017-01-17 introduction.tex
Polar irregularity figure added

\subsection{Plasma Structuring in the Polar Ionosphere}
\label{sec:polar_structure}
This thesis is concerned with the polar ionosphere, which is a particularly interesting and dynamic region due to the presence of open field lines to the solar wind.  The main focus of this work will be plasma density perturbations, often called irregularities.  Density irregularities in the polar cap can occur on scales ranging from thousands of kilometers to less than a centimeter \citep{Tsunoda1988}.  Large-scale plasma irregularities are typically considered to be any density structure on the scale of greater than 30 km \citep{Kelley2009}.  Some common examples are polar patches, polar holes, and sun-aligned arcs.  Polar patches are large density enhancements (usually at least twice the background plasma density) that travel across the polar cap with the background convection \citep{Weber1984,Valladares1994}.  Polar holes are plasma density depletions that typically occur in the \(F\) region slightly poleward of the auroral oval \citep{Benson2001}.  Sun-aligned arcs are large density forms that stretch across the polar cap along the sun-earth line.  They are very narrow and often characterized by large and complex velocity shears on either side of the arc \citep{Valladares1991}.

@@

Small-scale structuring is generally considered to be all irregularities less than 100 m \citep{Kelley2009}.  Although small-scale irregularities are not responsible for scintillation that directly impact GPS/GNSS performance, they can be the easiest to study because of large data sets collected from high frequency ionospheric radars globally for several decades (discussed further in Section \ref{sec:superdarn}).  The irregularity classifications presented here are rough categories only and a high degree of coupling between different scales occurs, which makes plasma structures of all scales (large, intermediate, and small) important for plasma structuring processes.  For instance, large-scale structures such as polar patches may very well have internal intermediate- and/or small-scale structuring.  A turbulent cascade is often assumed to connect these different scales, but because various instruments or techniques usually only observe structuring on a particular scale, it is difficult to find direct evidence of this or how exactly it occurs \citep{Kinter1985,Tsunoda1985}.  A description of some of the particular instruments and models that are used in this thesis follows.

>>>>

\subsection{Plasma Structuring in the Polar Ionosphere}
\label{sec:polar_structure}

This thesis is concerned with the polar ionosphere, which is a particularly interesting and dynamic region due to the presence of open field lines to the solar wind.  The main focus of this work will be plasma density perturbations, often called irregularities.  Density irregularities in the polar cap can occur on scales ranging from thousands of kilometers to less than a centimeter \citep{Tsunoda1988}, and a summary of some of these irregularities is presented in Figure \ref{fig:polarirreg}.  Large-scale plasma irregularities are typically considered to be any density structure on the scale of greater than 30 km \citep{Kelley2009}.  Some common examples are polar patches, polar holes, and sun-aligned arcs.  Polar patches are large density enhancements (usually at least twice the background plasma density) that travel across the polar cap with the background convection, Figure \ref{fig:polarirreg} \citep{Weber1984,Valladares1994}.  Polar holes are plasma density depletions that typically occur in the \(F\) region slightly poleward of the auroral oval \citep{Benson2001}.  Sun-aligned arcs are large density forms that stretch across the polar cap along the sun-earth line.  They are very narrow and often characterized by large and complex velocity shears on either side of the arc \citep{Valladares1991}.  Large scale plasma structures and the density gradients that surround them often serve as a platform for smaller-scale structures to form as well.  Polar patches, for instance, are known to form large finger-like structures along their trailing edges, Figure \ref{fig:polarirreg} \citep{Gondarenko2004,Hosokawa2016}.

\begin{figure}
	\includegraphics[width=0.8\textwidth]{irregularity.pdf}
	\caption{Schematic of different scale size plasma density irregularities that occur in the polar cap.  Polar patches, orange, move with the background ionospheric convection, indicated by green contours.  Field-aligned irregularities, FAIs, are density perturbations that form along the magnetic field lines, pink lines.}
	\label{fig:polarirreg}
\end{figure}

@@

Small-scale structuring is generally considered to be all irregularities less than 100 m \citep{Kelley2009}.  Although small-scale irregularities are not responsible for scintillation that directly impact GPS/GNSS performance, they can be the easiest to study because of large data sets collected from high frequency ionospheric radars globally for several decades (discussed further in Section \ref{sec:superdarn}).  Because electrons move far more easily along magnetic field lines than across them, density perturbations tend to be aligned with the magnetic field and are often known as field-aligned irregularities (FAI), Figure \ref{fig:polarirreg}.  The irregularity classifications presented here are rough categories only and a high degree of coupling between different scales occurs, which makes plasma structures of all scales (large, intermediate, and small) important for plasma structuring processes.  For instance, large-scale structures such as polar patches may very well have internal intermediate- and/or small-scale structuring.  A turbulent cascade is often assumed to connect these different scales, but because various instruments or techniques usually only observe structuring on a particular scale, it is difficult to find direct evidence of this or how exactly it occurs \citep{Kinter1985,Tsunoda1985}.  A description of some of the particular instruments and models that are used in this thesis follows.
